A Software Engineering Perspective on \\ OpenMP and PThreads

### 2017-10-11 sections/03-background.tex
More text Revisions.
active voice

Different approaches have been proposed to study the selection of the best level of
abstraction for teaching Parallel and Distributed programming courses.
Falcao~\cite{6565518} argues that introducing a high-level parallel programming
interface such as \textit{OpenMP} in the beginning of an undergraduate computer
science course would cause a small overhead and benefit the rest of the course.
Foley \textit{et al.}~\cite{FOLEY2017138} support the introduction of practical
learning experiences along an undergraduate course, of increasing depth as the
course progresses. They introduce OnRamp, a web application to help students
learn to write parallel code starting with practical and moving to conceptual
experiences.  Pllana \textit{et al.}~\cite{Pllana:2009} adopt a Model Driven
Development approach to develop parallel solutions using Parallel Building
Blocks. They introduce a programming environment that transforms these
high-level models in source code. The tool's goal is to hide from the students
the complexity of writing parallel code.

@@

In this paper we present data that supports the importance of composing a
curriculum for Parallel and Distributed Computing courses using low-level
programming interfaces, such as \textit{Pthreads}, as well as high-level
interfaces, such as \textit{OpenMP}.  Brown \textit{et
al.}~\cite{Brown:2010:SPC:1971681.1971689}, points that the choice of a
software tool should be only one of the topics explored during a parallel
programming course. Topics such as data structures, algorithms, software design
and parallel hardware platforms should also be explored.

>>>>

Several authors proposed different approaches to study the selection of the best
level of abstraction for teaching Parallel and Distributed programming courses.
Falcao~\cite{6565518} argues that introducing a high-level parallel programming
interface such as \textit{OpenMP} in the beginning of an undergraduate computer
science course would cause a small overhead and benefit the rest of the course.
Foley \textit{et al.}~\cite{FOLEY2017138} support the introduction of practical
learning experiences along an undergraduate course, of increasing depth as the
course progresses. They introduce OnRamp, a web application to help students
learn to write parallel code starting with practical and moving to conceptual
experiences.  Pllana \textit{et al.}~\cite{Pllana:2009} adopt a Model Driven
Development approach to develop parallel solutions using Parallel Building
Blocks. They introduce a programming environment that transforms these
high-level models in source code. The tool's goal is to hide from the students
the complexity of writing parallel code.

@@

In this paper we present data that supports the importance of composing a
curriculum for Parallel and Distributed Computing courses using low-level
programming interfaces, such as \textit{Pthreads}, as well as high-level
interfaces, such as \textit{OpenMP}.
